Garbage Collection Evaluation Infrastructure\\ for the Cog VM

### 2018-06-20 paper.tex
Fix Vm => VM
Use a concise cliche

\paragraph{Release.} The Release benchmark releases all the graphs. With the compacting GC, memory goes back to its original size. With Sweep, multiple memory segments are left with a few live objects, preventing the Vm from returning those segments to the OS. Hence, the memory decreases drastically, but not to the original size. Compaction time is much faster with Sweep, but as we have discussed, for less efficiency. Changing Eden size has not much, if any, impact here, since it's essentially a pure full GC benchmark.

>>>>

\paragraph{Release.} The Release benchmark releases all the graphs. With the compacting GC, memory goes back to its original size. With Sweep, multiple memory segments are left with a few live objects, preventing the VM from returning those segments to the OS. Hence, the memory decreases drastically, but not to the original size. Compaction time is much faster with Sweep, but as we have discussed, for less efficiency. Changing Eden size has little if any impact here, since it's essentially a pure full GC benchmark.
